Practical Optional Types for Clojure

### 2015-02-24 formal-model.tex
experience intro

Typing rules are given in figure~\ref{main:figure:hmaptyping}. T-GetHMap handles the simple
case where we know a lookup will succeed and use B-Get. In T-GetHMapAbsent we know B-GetMissing will give
a \Nil{} return type.
T-GetHMapPartialDefault does not know if the key is present or absent and has a \Top{} return type.
T-Assoc extends the known keyword entries, overwriting previous entries with the same key.

@@

@@

\begin{figure*}
  $$
\begin{array}{lllll}
\updatefigure
\end{array}
$$
\caption{Type Update}
\end{figure*}
}

>>>>

Typing rules are given in figure~\ref{main:figure:hmaptyping}. T-GetHMap handles the simple
case where we know a lookup will succeed and use B-Get. In T-GetHMapAbsent we know B-GetMissing will give
a \Nil{} return type.
T-GetHMapPartialDefault does not know if the key is present or absent and has a \Top{} return type.
Even though their types vary significantly, we still use the same object.
T-Assoc extends the known keyword entries, overwriting previous entries with the same key.

@@

\subsection{Proof system}

The essential piece of occurrence typing's logical system is L-Update.
(The metavariable \propisnotmeta{} ranges over \t{} and \nottype{\t{}} (without variables).)

\begin{mathpar}
{\LUpdate}
\end{mathpar}

This is where we combine propositions with similar objects
to learn new facts.
The full definition of \updateliteral{} is given
in

\begin{figure*}
  $$
\begin{array}{lllll}
\updatefigure
\end{array}
$$
\caption{Type Update}
\end{figure*}

@@
